### 2025-02-28 paper/conclusions.tex
Word fiddling.

The paper demonstrates a technique of developing high performance
applications with strong correctness guarantees, including the absence
of out-of-bound indexing, certain functions being inverses,
well-scopedness and well-typedness of the embedded DSL and
semantics-preserving optimisations.

@@

Having a trusted specification as well as entire code-generation
pipeline within a single dependently-typed framework is incredibly
powerful. As we have demonstrated at the example of the neural
network, we can introduce domain-specific optimisations and
transformations, such as automatic differentiation. For our example,
the entire framework that includes array theory, DSL, optimisations
and extraction is about 2000 lines of Agda code.

>>>>

We have demonstrated a technique of developing high performance
applications with strong correctness guarantees, including the absence
of out-of-bound indexing, certain functions being inverses,
well-scopedness and well-typedness of the embedded DSL, and
semantics-preserving optimisations.

@@

Having a trusted specification as well as entire code generation
pipeline within a dependently-typed framework is incredibly
powerful. As we have demonstrated at the example of the neural
network, we can introduce domain-specific optimisations and
transformations, such as automatic differentiation. For our example,
the entire framework that includes array theory, DSL, optimisations
and extraction is about 2000 lines of Agda code.
